---
title: "Turorial"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    df_print: default
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library(learnr)

tutorial_options(
  exercise.timelimit = 60,
  exercise.eval = TRUE
)

# Code that prints anything to the console should be at the end of any one chunk
knitr::opts_chunk$set(
  echo = FALSE,
  # Can't be set in tutorial_options()
  exercise = TRUE,
  # Problematic arguments: If not set this way, output breaks code
  results = "hold",
  collapse = FALSE,
  error = FALSE,
  warning = FALSE,
  message = FALSE
)
```






# trainr


The goal of trainr is to create interactive exercises from static 'rmarkdown' documents.

Reproducible but static 'rmarkdown' documents abound. For example, many R
packages include them in README.Rmd and vignettes. You can transform each
'rmarkdown' code chunk into an R console using the learnr exercises
(<https://rstudio.github.io/learnr/exercises.html>). But the transformation can
be tedious (e.g. label unlabeled code chunks and chain exercises setup). This
package automates the process.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/trainr")
```
## Example

```{r example, exercise.setup='setup'}
library(trainr)
```

Transform the static README.Rmd of this package into an interactive 'learnr' tutorial, where each executable code chunk is an exercises -- i.e. an R console.

```{r unlabeled-47, exercise.setup='example'}
url <- "https://raw.githubusercontent.com/maurolepore/trainr/master/README.Rmd"
```

Have a look to this file as is:

```{r unlabeled-53, comment="", exercise.setup='unlabeled-47'}
writeLines(readLines(url))
```

Convert each executable chunk to an 'learnr' exercise.

```{r unlabeled-59, exercise.setup='unlabeled-53'}
path <- tempfile(fileext = ".Rmd")
write_tutorial(url, path)
```

Have a look to this file after the transformation.

```{r unlabeled-66, comment="", exercise.setup='unlabeled-59'}
writeLines(readLines(path))
```

Enjoy!

```r
rmarkdown::run(path)
```

## Avoid problems

Code that prints anything to the console should be at the end of any one chunk.

* Good:

```{r unlabeled-82, exercise.setup='unlabeled-66'}
x <- 1
message("Good: Output something to the console at the end of the code chunk")
```

* Bad:

```{r unlabeled-89, exercise.setup='unlabeled-82'}
message("Bad: Output something to the console before the end of the code chunk")
x <- 1
```

* Also bad:

```{r unlabeled-96, exercise.setup='unlabeled-89'}
x <- 1
# Bad: Output something to the console before the end of the code chunk
x
y <- 2
```

