---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# trainr

<!-- badges: start -->
<!-- badges: end -->

The goal of trainr is to create interactive exercises from static 'rmarkdown' documents.

Reproducible but static 'rmarkdown' documents abound. For example, many R
packages include them in README.Rmd and vignettes. You can transform each
'rmarkdown' code chunk into an R console using the learnr exercises
(<https://rstudio.github.io/learnr/exercises.html>). But the transformation can
be tedious (e.g. label unlabeled code chunks and chain exercises setup). This
package automates the process.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("maurolepore/trainr")
```
## Example

```{r example}
library(trainr)
```

Transform the static README.Rmd of this package into an interactive 'learnr' tutorial, where each executable code chunk is an exercises -- i.e. an R console.

```{r}
url <- "https://raw.githubusercontent.com/maurolepore/trainr/dump-features/README.Rmd"
```

Have a look to this file as is:

```{r, results='asis'}
writeLines(head(readLines(url), 20))
```

Convert each executable chunk to an 'learnr' exercise.

```{r}
path <- tempfile(fileext = ".Rmd")
write_tutorial(url, path)
```

Have a look to this file after the transformation.

```{r, results='asis'}
writeLines(head(readLines(path), 20))
```
